% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TEX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,12pt,oneside]{article}
%\documentclass[letterpaper,10pt,oneside]{article}

% Do not stop on errors during compilation.
%\nonstopmode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVTitle}{Liang-Bo Wang's CV}
\newcommand{\CVNote}{Last updated: {\today}}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={Liang Bo Wang},
pdfsubject={http://liang2.tw},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{Liang-Bo Wang}

\begin{subtitle}
%\href{https://www.google.com/maps/place/17+Prime+Avenue,+Springfield,+Pennsylvania+10111,+USA}
%{17 Prime Avenue, Apt 37, Springfield, Pennsylvania 10111, USA}
%\par
\href{mailto:liang-bo.wang@wustl.edu}
{liang-bo.wang@wustl.edu}
\,\BulletSymbol\,
+1 (314) 285-8111
\,\BulletSymbol\,
\href{https://blog.liang2.tw}
{https://blog.liang2.tw}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section{Education}
{Education}
{PDF:Education}


\href{https://wustl.edu/}
{\textbf{Washington University in St. Louis}},
United States
\par
\textbf{Ph.D. candidate} in
\href{http://dbbs.wustl.edu/divprograms/compbio/Pages/default.aspx}
{Computational and Systems Biology}
\hfill
\DatestampYM{2016}{08} --
(present)

\BigEntryGap

\href{http://www.ntu.edu.tw/english/index.html}
{\textbf{National Taiwan University}},
Taipei, Taiwan
\par
\textbf{M.S.} in
\href{http://www.bebi.ntu.edu.tw/English/index.html}
{Biomedical Electronics and Bioinformatics}
\hfill
\DatestampYM{2014}{01} --
\DatestampYM{2016}{06}
% \begin{detail}
%     \begin{detailitem}
%     \item GPA: 3.85 / 4.0
%     \end{detailitem}
% \end{detail}


\EntryGapNoBreak
\textbf{B.S.} in
\href{http://www.ee.ntu.edu.tw/en/}
{Electrical Engineering}
\hfill
\DatestampYM{2009}{09} --
\DatestampYM{2014}{01}
\par
Minor in Economics
% \begin{detail}
%     \begin{detailitem}
%     \item Minor in Economics
%     \item GPA: 3.79 / 4.0
%     \end{detailitem}
% \end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards\newline\& Scholarships}
{Awards \& Scholarships}
{PDF:Awards \& Scholarships}

\href{https://global.wustl.edu/mcdonnell-academy/}
{\textbf{McDonnell International Scholars Academy}}
\hfill
\DatestampY{2016} --
Present
\par
Washington University in St. Louis

\EntryGapNoBreak
\textbf{Outstanding Summer Research Award}
\hfill
\DatestampY{2012}
\par
Center of Genomic Medicine, National Taiwan University
% \begin{detail}
%     \begin{detailitem}
%     \item Research Topic: miRNA discovery using NGS data
%     \end{detailitem}
% \end{detail}

% \EntryGapNoBreak
% \textbf{Gold medal},
% International Genetically Engineered Machine (iGEM)
% \hfill
% \DatestampY{2012}
% \begin{detail}
%     \begin{detailitem}
%     \item Topic: A demonstration of PepdEx with mind-altering bacteria
%     \item Role: Biological circuit (gene network) simulation and wiki page construction
%     \end{detailitem}
% \end{detail}


%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\textbf{PhD Thesis},
Washington University in St. Louis
\hfill
\DatestampYM{2017}{05} --
(present)
\par
\begin{detail}
    \begin{detailitem}
    \item Advisor: Dr. Li Ding
    \item Topic: Proteogenomic and Spatial Characterization of Glioblastoma Tumors at Bulk and Single Cell Level
    \end{detailitem}
\end{detail}


\BigEntryGapNoBreak
\textbf{Microsoft Research Asia},
Beijing, China
\hfill
\DatestampYM{2014}{07} --
\DatestampYM{2015}{02}
\par
Internship
\begin{detail}
    \begin{detailitem}
    \item Advisor: Dr. Eric Chang
    \item Topic: Cancer Image and Pathway Analysis
    \item Applied convolutional neural network to histopathology image analysis
    \end{detailitem}
\end{detail}


\BigEntryGapNoBreak
\textbf{Biomedical Engineering and Bioinformatics},
National Taiwan University
\par
Graduate Research
\hfill
\DatestampYM{2014}{01} --
\DatestampYM{2016}{06}
\begin{detailitem}
    \item Advisor: Professor Eric Y. Chuang
    \item Topic: Integrative analysis of copy number variation, gene expression, and miRNA regulation on cancer; drug treatment prediction on lung cancer cell line
\end{detailitem}


\EntryGapNoBreak
Undergraduate Research% (Advisor: Dr. Eric. Y. Chuang)
\hfill
\DatestampYM{2012}{09} --
\DatestampYM{2014}{01}
\begin{detail}
    \begin{detailitem}
    \item Advisor: Professor Eric Y. Chuang
    \item Topic: DNA-seq, RNA-seq and small RNA-seq data processing
    \item Project: \href{https://github.com/BioCloud-TW/nextbiopy}{Nextbiopy}, a web-based NGS pipeline report generator
    \end{detailitem}
\end{detail}

\EntryGapNoBreak
Undergraduate Research% (Advisor: Dr. Wei-Cheng Tian)
\hfill
\DatestampYM{2011}{09} --
\DatestampYM{2012}{11}
\begin{detail}
    \begin{detailitem}
    \item Advisor: Associate Professor Wei-Cheng Tian
    \item Project: CMOS-based tactile sensor system for blood pressure measurement
    \end{detailitem}
\end{detail}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
{Work Experience}
{PDF:Work Experience}

\href{http://pinkoi.com}
{\textbf{Pinkoi}},
Taipei, Taiwan
\hfill
\DatestampYM{2015}{06} --
\DatestampYM{2015}{09}
\par
Internship
\begin{detail}
    \begin{detailitem}
    \item Pinkoi is an online marketplace for unique and original design goods in Asia
    \item Topic: Product search improvement
    \item Improved Chinese text segmentation on ElasticSearch and added
        preliminary semantic search built on Word2Vec
    \end{detailitem}
\end{detail}


%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\section{Publications}
{Publications}
{PDF:Publications}

\subsection{Journals}
{Journals}
{PDF:Journals}

\begin{publication}[series=pub, widest*=100]
    \item
        \textbf{LB Wang}$^*$, A Karpova$^*$, MA Gritsenko$^*$, JE Kyle$^*$, S Cao$^*$, Y Li$^*$, \textit{et al.}
        ``Proteogenomic and Metabolomic Characterization of Human Glioblastoma.''
        \textit{Cancer Cell} 39 (4).
        \DatestampYM{2021}{02}

    \item
        F Petralia, \textit{et al.}
        ``Integrated Proteogenomic Characterization across Major Histological Types of Pediatric Brain Cancer.''
        \textit{Cell} 183 (7), 1962-1985.
        \DatestampYM{2020}{12}

    \item
        MH Bailey, \textit{et al.}
        ``Retrospective evaluation of whole exome and genome mutation calls in 746 cancer samples.''
        \textit{Nature Communications} 11 (1), 1-27.
        \DatestampYM{2020}{09}

    \item
        MA Gillette, \textit{et al.}
        ``Proteogenomic characterization reveals therapeutic vulnerabilities in lung adenocarcinoma.''
        \textit{Cell} 182 (1), 200-225.
        \DatestampYM{2020}{07}

    \item
        O Rozenblatt-Rosen, \textit{et al.}
        ``The Human Tumor Atlas Network: charting tumor transitions across space and time at single-cell resolution.''
        \textit{Cell} 181 (2), 236-249.
        \DatestampYM{2020}{04}

    \item
        JE McDermott, \textit{et al.}
        ``Proteogenomic Characterization of Ovarian HGSC Implicates Mitotic Kinases, Replication Stress in Observed Chromosomal Instability.''
        \textit{Cell Reports Medicine}, 1 (1) 100004.
        \DatestampYM{2020}{04}

    \item
        DJ Clark, \textit{et al.}
        ``Integrated proteogenomic characterization of clear cell renal cell carcinoma.''
        \textit{Cell} 179 (4), 964-983.
        \DatestampYM{2019}{10}

    \item
        GF Gao$^*$, JS Parker$^*$, SM Reynolds$^*$, TC Silva$^*$, \textbf{LB Wang}$^*$, W Zhou$^*$, \textit{et al.}
        ``Before and After: Comparison of Legacy and Harmonized TCGA Genomic Data Commons’ Data.''
        \textit{Cell Systems} 9 (1), 24-34.
        \DatestampYM{2019}{07}

    \item
        SQ Sun, RJ Mashl, S Sengupta, AD Scott, W Wang, P Batra, \textbf{LB Wang}, M A Wyczalkowski, L Ding.
        ``Database of evidence for precision oncology portal.''
        \textit{Bioinformatics} 34 (24), 4315-4317.
        \DatestampYM{2018}{07}.

    \item
        KL Huang, \textit {et al.}
        ``Pathogenic germline variants in 10,389 adult cancers.''
        \textit{Cell}, 173 (2), 355-370. e14.
        \DatestampYM{2018}{04}.

    \item
        Y Xu, Z Jia, \textbf{LB Wang}, Y Ai, F Zhang, M Lai, I Eric, C Chang.
        ``Large scale tissue histopathology image classification, segmentation, and visualization via deep convolutional activation features.''
        \textit{BMC Bioinformatics}, 18 (1), 281.
        \DatestampYM{2017}{12}.

    \item
        YP La$^*$, \textbf{LB Wang}$^*$, WA Wang$^*$, LC Lai, MH Tsai, TP Lu, E Y Chuang.
        ``iGC—an Integrated Analysis Package of Gene Expression and Copy Number Alteration.''
        \textit{BMC Bioinformatics}, 18 (1), 35.
        \DatestampYM{2017}{01}.

    \item
        \textbf{LB Wang}, E Y Chuang, TP Lu.
        ``Identification of predictive biomarkers for ZD-6474 in lung cancer.''
        \textit{Translational Cancer Research}, 4 (4), 324-331.
        \DatestampYM{2015}{08}.

    \item
        CY Lee$^*$, YC Chiu$^*$, \textbf{LB Wang}$^*$, YL Kuo$^*$, EY  Chuang, LC Lai, MH Tsai.
        ``Common applications of next-generation sequencing technologies in genomic research.''
        \textit{Translational Cancer Research}, 2 (1), 33-45.
        \DatestampYM{2013}{02}.
\end{publication}

\BigEntryGap
\subsection{Conference Papers}
{Conferences Papers}
{PDF:Conference Papers}

\begin{publication}[widest*=100]  %resume=pub to resume the publication counter

    \item
        CT Sun, YC Lin, CJ Hsieh, JC Liou, \textbf{LB Wang}, WC Tian.
        ``A linear-response CMOS-MEMS capacitive tactile sensor'',
        \textit{IEEE Sensors 2012},
        Taipei, Taiwan,
        \DatestampYM{2012}{10}.

\end{publication}


%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section{Programming Skills}
{Programming Skills}
{PDF:Programming Skills}

\subsection{Languages}
{Languages}
{PDF:Languages}

Python (both scientific and web stack),
R,
Web frontend (HTML/CSS/Javascript),
SQL,
C

% \subsection
% {Tools}
% {Tools}
% {PDF:Tools}
%
% \begin{detail}
%     \begin{detailitem}
%     \item Bioinfo: samtools, seqtk, FastQC, Tophat
%     \item Python: Numpy, Scipy, Pandas, sckit-learn, matplotlib, seaborn, gensim, Django, Flask, Bottle
%     \item R: rpy2, ggplot2, (d)plyr, data.tables
%     \item Database: PostgreSQL, SQLite
%     \item OS: Debian Linux, OSX
%     \end{detailitem}
% \end{detail}

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\section{Community Engagement}
{Community Engagement}
{PDF:Community Engagement}

\href{http://pycon.tw}{\textbf{PyCon Taiwan}} Organizing Committee, Taipei, Taiwan
\hfill
\DatestampYM{2015}{07} --
\DatestampYM{2016}{07}
\par
Program Committee Chair

\EntryGapNoBreak
\href{http://pycon.tw}{\textbf{PyCon APAC}} Organizing Committee, Taipei, Taiwan
\hfill
\DatestampY{2014},
\DatestampY{2015}
\par
Public Relations Manager

\BigEntryGapNoBreak
\textbf{Open Source Communities}, Taipei, Taiwan
\hfill
\DatestampY{2013} --
\DatestampY{2016}
\par
Regular Speaker
\begin{detail}
    \begin{detailitem}
    \item Including Taiwan PyCon, Taipei.py, Taiwan R User Group, and PyCon China
    \item Gave over \href{http://blog.liang2.tw/talks/#talks}{10 talks}, topics included
        convolutional neural network, text search,
        HDF5, parallel computing, and R ggplot2 plotting.
    \end{detailitem}
\end{detail}

% \BigEntryGap
% \textbf{Photography Club},
% National Taiwan University
% \hfill
% \DatestampY{2009} --
% \DatestampY{2013}
%
% President
% \hfill
% \DatestampYM{2011}{03} --
% \DatestampYM{2011}{09}
%
% Leader of Education Division
% \hfill
% \DatestampYM{2010}{03} --
% \DatestampYM{2011}{03}
%
% \BigEntryGap
% \textbf{Summer Camp for High School},
% \hfill
% \DatestampY{2011},
% \DatestampY{2012}
% \par
% Electrical Engineering, National Taiwan University
%
% Leader of the Photography Division
% \begin{detail}
%     \begin{detailitem}
%     \item Recorded, wrote and produced television news and newspaper per day about camp activities
%     \end{detailitem}
% \end{detail}
\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\begin{flushright}
\scriptsize%
[\textit{\CVNote}]%
\hspace{2.0mm}\null
\end{flushright}

\label{LastPage}
\end{document}
