% !TeX root = ../resume.tex
\section{Experience}
\begin{entrylist}

\item \textbf{Moderna} \hfill Cambridge, MA\\
Sr. Scientist, Oncology Bioinformatics \hfill
Mar 2025--Present\\
Scientist, Oncology Bioinformatics \hfill
Apr 2023--Mar 2025
\begin{detaillist}
    \item Led integration of diverse omics tools and algorithms to advance personalized cancer vaccine development (Individualized Neoantigen Therapy; \href{https://en.wikipedia.org/wiki/MRNA-4157/V940}{INT}).
    \item Collaborated closely with engineering team to develop and validate end-to-end Nextflow pipeline for personalized cancer vaccine design, meeting critical timelines for regulatory review.
    \item Led implementation of key NGS quality control metrics in cancer vaccine related bioinformatic pipelines to meet compliance with regulatory agencies and internal performance evaluation.
\end{detaillist}

\item \textbf{Mandatory National Service} \hfill Taipei, Mar 2022--Mar 2023

\item \textbf{Washington University in St. Louis} \hfill St. Louis, MO\\
PhD Research, \href{https://dinglab.wustl.edu/}{Li Ding Lab} \hfill
May 2017--Dec 2021
\begin{detaillist}
    % \item Thesis: Building a toolbox and insights toward proteogenomic characterization of glioblastoma
    \item Characterized human tumor using mass spectrometry, single cell sequencing, spatial transcriptomics, multiplexed imaging, and other high-throughput technologies.
    \item Member of large-scale cancer research communities including The Cancer Genome Atlas (TCGA), Clinical Proteogenomic Tumor Analysis Consortium (CPTAC), and Human Tumor Atlas Network (HTAN).
    \item Led the data analysis team of CPTAC glioblastoma study, coordinating collaboration across institutions nationwide.
    % \item Developed tools and databases (\href{https://ptmcosmos.wustl.edu/}{PTMcosmos}, \href{https://github.com/ding-lab/CharGer}{CharGer}) to analyze large-scale multi-modal datasets
\end{detaillist}

\item \textbf{Open Source Software}
Contributor \hfill 2015--Present
\begin{detaillist}
    \item Contributed to tools and projects including conda-forge, bioconda, and cyvcf2.
    \item Familiar with R \& Python software development process (testing, packaging, CI/CD, and documentation).
\end{detaillist}

\item \href{http://pinkoi.com}{\textbf{Pinkoi}} Internship \hfill Taipei, Summer 2015
\begin{detaillist}
    \item Improved e-commerce product search by improving Mandarin text segmentation and adopting Word2vec semantic search.
\end{detaillist}

\item \textbf{Microsoft Research Asia} Research Internship \hfill Beijing, Jul 2014--Feb 2015
\begin{detaillist}
    \item Applied deep learning to cancer histopathology image and pathway analysis.
\end{detaillist}

% \item \textbf{National Taiwan University} \hfill Taipei\\
% Master's Research, Eric Y. Chuang Lab \hfill
% 2014--2016
% \begin{detaillist}
%     \item Developed a cloud platform to process and analyze sequencing data
% \end{detaillist}

\end{entrylist}
